Energy and the CES production function

### 2016-06-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now saving and loading ReModels. No longer loading and operating on EcolEcon2015kleResampleModelsCES.rds, because it can be a HUGE file, especially with 1000 resamples.

resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
if (rerunResampling){
  # Run some resampling on the PT and UK models that reject the cost-share theorem,
  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
  # This is u-g-l-y code. Just getting something running for now.
  modPT <- models$PT$adjusted$withE$CES$kle
  modUK <- models$UK$adjusted$withE$CES$kle
  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
  # Resample models
  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
  # Resample coefficients
  resampleCoeffsCES <- bind_rows(
    bind_cols(resamplesCESPT$coeffs %>% mutate(Country="PT")), 
    bind_cols(resamplesCESUK$coeffs %>% mutate(Country="UK")))
  resampleCoeffsCES$energy <- TRUE
  resampleCoeffsCES$nest <- "(kl)e"
  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
} else {
  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
  resampleModelsCES <- readRDS(resampleModelsCESFilename)
}
@

<<ReModels>>=
ReModels <-
  bind_rows(
  leaf_apply(resampleModelsCES, 
             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
             strict.lists = TRUE)
)
@

>>>>

resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
ReModelsFilename <- "ReModels.rds"
if (rerunResampling){
  # Run some resampling on the PT and UK models that reject the cost-share theorem,
  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
  # This is u-g-l-y code. Just getting something running for now.
  modPT <- models$PT$adjusted$withE$CES$kle
  modUK <- models$UK$adjusted$withE$CES$kle
  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
  # Resample model objects
  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
  # Save this object in case we need to interrogate it later.
  # Note, however, that resampleModelsCES is NOT in the repository,
  # because it can be a HUGE file when we're doing, say, 1000 resamples.
  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
  # Resample time series
  ReModels <-
    bind_rows(
      leaf_apply(resampleModelsCES, 
                 function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
                 strict.lists = TRUE)
    )
  saveRDS(ReModels, file = ReModelsFilename)
  # Resample coefficients
  resampleCoeffsCES <- bind_rows(
    bind_cols(resamplesCESPT$coeffs %>% mutate(Country="PT")), 
    bind_cols(resamplesCESUK$coeffs %>% mutate(Country="UK")))
  resampleCoeffsCES$energy <- TRUE
  resampleCoeffsCES$nest <- "(kl)e"
  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
} else {
  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
  # We don't need to load resampelModelsCES, because we use only ReModels later.
  # resampleModelsCES <- readRDS(resampleModelsCESFilename)
  ReModels <- readRDS(ReModelsFilename)
}
@

% <<ReModels>>=
% # ReModels is the data frame that holds time series of all the resample models.
% # We save this to disk and include it in the repo, because it is much smaller than resampleModelsCES.
% if (! rerunResampling){
%   ReModels <- readRDS(ReModelsFilename)
% } else {
%   # This code is expensive, so run only if we re-ran the resampling.
%   ReModels <-
%     bind_rows(
%       leaf_apply(resampleModelsCES, 
%                  function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
%                  strict.lists = TRUE)
%     )
% }
% @
